%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                HE MING LIU RESUME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt,letterpaper]{article}
\usepackage{geometry}   
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{comment}
\usepackage{setspace}

\pagenumbering{gobble} % turns off page numbering

% Margins
\geometry{
    top=0.5in,
    bottom=0.5in,
    left=0.5in,
    right=0.5in
}
\setstretch{1.1}
\setlist{left=0.5em, itemsep=-0.3em, topsep=0em}

% Section Formatting
\usepackage{titlesec}
\titleformat
    {\section}
    [hang]
    {\vspace*{-1.5em}\Large\scshape}
    {}
    {0em}
    {}
    [{\titlerule[0.05em] \vspace*{-0.3em}}]

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                    HEADER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\huge{\textbf{He Ming (Andy) Liu}} \\
\vspace*{0.5em}
\small{{\href{tel:6476155622}{+1 (647)-615-5622}}
        \hspace{0.5em} \textbar \hspace{0.5em}
        \href{mailto: liuandy1207@gmail.com}{liuandy1207@gmail.com}
        % \href{mailto: heming.liu@mail.utoronto.ca}{heming.liu@mail.utoronto.ca}
        \hspace{0.5em} \textbar \hspace{0.5em}
        \href{https://www.linkedin.com/in/liuandy1207/}{linkedin.com/in/liuandy1207}}
        \hspace{0.5em} \textbar \hspace{0.5em}
        \href{https://github.com/liuandy1207}{github.com/liuandy1207}
\end{center} \vspace{-0.7em}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%












%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                    EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

%*************************************************
\textbf{University of Toronto} \hfill
Sep 2024 - Apr 2029 (Expected) \\
\textit{Bachelor of Applied Science in Engineering Science + PEY Co-Op} \hfill 
cGPA: 3.57, Dean's List
\begin{itemize}
    \item \underline{Relevant Coursework}: Electric Circuits, Computer Systems (SystemVerilog, Assembly), Deep Learning (PyTorch), ODEs
\end{itemize} \vspace{0.5em}
%---------------- Coursework  --------------------
%   Struct. \& Materials (MATLAB)
%   Praxis (Onshape)
%   Eng. Math \& Comp. (MATLAB)
%   Classical Mechanics
%   Fund. of Elec. Circuits
%   Calculus
%   Linear Algebra
%   Molecules \& Materials
%   Vector Calc. \& Fluid Mechanics
%   Thermodynamics
%   Digital \& Computer Sys. (SystemVerilog, Assembly)
%   ODEs
%   Waves \& Modern Physics
%*************************************************

%*************************************************
\raggedright
\textbf{University of Waterloo} \hfill
Sep 2023 - Aug 2024 \\
\textit{Bachelor of Math in Mathematics/Financial Analysis and Risk Management} \hfill
cGPA: 3.79
\begin{itemize}
    \item \underline{Relevant Coursework}: Elementary Algorithm Design \& Data Abstraction (C), Tools \& Techniques for Software Dev. (CLI, Scripting, Git), Designing Functional Programs (Racket), Honours Linear Algebra, Public Speaking
\end{itemize}
%---------------- Coursework  --------------------
%   Elementary Algorithm Design (C)
%   Intro to Financial Markets
%   Public Speaking
%   Designing Functional Programs (Racket)
%   Honours Algebra
%   Honours Calculus
%   Intro to Financial Accounting
%   Elementary Algorithm Design \& Data Abstraction (C)
%   Tools \& Techniques for Software Dev. (CLI, Scripting, Git)
%   Honours Linear Algebra
%*************************************************   
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%













%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                    SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}

\hspace{0.75em}\textbf{Programming Languages:} Python (PyTorch), C, C++, Java, MATLAB, RISC-V Assembly, JavaScript, Racket \\
%-------------- Programming Languages  -----------
%   C
%   C++
%   Java
%   JavaScript
%   MATLAB
%   Python
%   Racket
%   RISC-V Assembly
%-------------------------------------------------

\hspace{0.75em}\textbf{Engineering Tools:} CAD, Git \& GitHub, HTML \& CSS, LaTeX, Microsoft Office (Excel), CLI, Scripting \\
%---------------- Engineering Tools  -------------
%   CLI
%   CAD
%   Git \& GitHub
%   HTML \& CSS
%   LaTeX
%   Microsoft Office (Excel)
%   Scripting
%-------------------------------------------------
\hspace{0.75em}\textbf{Embedded Systems:} Arduino, ESP32, MicroPython, CircuitPython, SystemVerilog, Altium, KiCad \\
%---------------- Embedded Systems  -------------
%   Altium
%   Arduino
%   CircuitPython
%   ESP32
%   KiCad
%   MicroPython
%   SystemVerilog
%-------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%






%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                    PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

%*************************************************  
%                 Resonant Evil
%************************************************* 
\textbf{Theme Prize Winner - Resonant Evil - Audio-Based Maze Escape Arcade Game} \hfill Feb 2025 \\
\begin{itemize}
    \item Won the Video Games Theme Prize at MakeUofT 2025, Canada's largest makeathon, outperforming 300+ participants. 
    \item Developed an immersive audio-driven Arduino arcade machine game to increase accessibility for the visually impaired.
    \item Implemented dynamic audio and haptic feedback that guided player navigation and heightened tension. 
    \item Built a BFS-based maze generator that allowed fair monster pathfinding and ensured solveability. 
\end{itemize}
%************************************************* 



%************************************************* 
%                Wannabe WALL-E
%************************************************* 
\vspace*{0.5em}
\textbf{First Place Winner - Wannabe WALL-E - Autonomous Vehicle Challenge} \hfill Feb 2025 \\
\begin{itemize}
    \item Won 1st place in the UTRAHacks 2025 Autonomous Vehicle Challenge, outperforming 250+ participants. 
    \item Developed an Arduino autonomous robot that used ultrasonic and IR sensors to navigate through a series. 
    \item Engineered a corrective turning algorithm to compensate for a malfunctioning motor driver, preventing critical failure. 
\end{itemize}
%************************************************* 




%************************************************* 
%                Silent Night
%************************************************* 
\vspace*{0.5em}
\textbf{Theme Prize Winner - Silent Night - IoT Smart Pillow} \hfill Feb 2024 \\
\begin{itemize}
    \item Won the Smart Home Tech Theme Prize at MakeUofT 2024, beating 300+ participants.  
    \item Designed an IoT smart pillow to monitor sleep conditions and correct posture using an ESP32.
    \item Built a posture-adjustment system to improve sleep ergonomics through automated microcorrections. 
\end{itemize}
%*************************************************
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

















%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                    EXPERIENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiences}

%************************************************* 
%                     IEEE
%************************************************* 
\textbf{IEEE - University of Toronto Branch} \hfill 
Toronto, ON \\
\textit{Project Lead + Tech Associate} \hfill
Aug 2025 - Present \\
\begin{itemize}
\item Devised the sensing-to-feedback pipeline linking OpenCV object detection and sensor readings to ESP32 dynamic haptic feedback, enabling real-time navigation support for the visually impaired. 
\item Coordinated cross-function contributions on the Smart Cane Project, ensuring steady progress. 
\item Co-hosted a Git workshop for 100+ hackathon participants, introducing them to VCS fundamentals.
\end{itemize}
%************************************************* 

%************************************************* 
%                     CAROBOT
%************************************************* 
\textbf{CAROBOT Learning and Research Organization} \hfill
Markham, ON \\
\textit{Engineering Trainee} \hfill 
May 2025 - Aug 2025 \\
\begin{itemize}
    \item Designed a youth robotics curriculum revolving around the \textbf{ESP32}, enabling beginners to explore the field with simplified programming through BIPES (block-based) and MicroPython.
    \item Contributed to building a fully-functional, offline web-based version of the BIPES IDE, improving accessibility for classrooms without reliable internet or download permissions.
\end{itemize}
%************************************************* 

%%%%%%


\begin{comment}
\textbf{Private Universe - Short Film Production}
\hfill
Taipei, Taiwan
\\
\textit{Line Producer + Actor}
\hfill
May 2024 - Aug 2024 \\
\vspace{-5pt}
\begin{itemize}[left=0.5em, itemsep=-3pt]
 \item Coordinated with cast and crew to streamline operations and meet tight deadlines.

    \item Performed in a key role as an alien, contributing to both the creative and technical aspects of the film.
\end{itemize}
%%%%%%


\textbf{UW Financial Analysis \& Risk Management Student Association (FARMSA)}
\hfill
Waterloo, ON
\\
\textit{Internal Analyst + IT Analyst}
\hfill
Sep 2023 - Apr 2024 \\
\vspace{-5pt}
\begin{itemize}[left=0.5em, itemsep=-3pt]
 \item Revamped the FARMSA website using JavaScript, HTML, and CSS to improve SEO, UX, and accessibility for hundreds of FARM students.
 \item Organized networking events and technical workshops that enhanced student engagement and professional development.
\end{itemize}
%%%%%%
\end{comment}

\begin{comment}
\textbf{Unionville High School Student Council}
\hfill
Markham, ON
\\
\textit{Grade 11, 12 Representative + Mascot}
\hfill
Oct 2021 - June 2023 \\
\vspace{-5pt}
\begin{itemize}[left=0.5em, itemsep=-3pt]
\item Coordinated a club fair for 500+ students and hosted monthly meetings with club leaders.  
\item Represented school spirit as the official mascot, engaging students and energizing events.  
\end{itemize}
\end{comment}




















\end{document}
